%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {\href{https://nikhil-bhasin.netlify.app/data/LetterOfExperience_Innovaccer.pdf}{Software Development Engineer - Intern}} % Job title
    {\href{https://innovaccer.com/}{Innovaccer}} % Organization
    {Noida, India} % Location
    {May. 2021 - Sep. 2021} % Date(s)
     {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked in an Agile Development Environment in the InAPI Product Engineering Team to develop the production-ready Backend services of \href{https://www.hl7.org/fhir/index.html}{\textbf{FHIR} Server}, FHIR Analytics Server, Data Migration Pipeline, and Data Quality Report.}
        \item {Responsible for RESTful API Design and Development, OpenAPI Documentation, Request Validation, Test-Driven Development, Logging and Debugging.}
        \item {Created optimised and scalable Back-end services of Data Quality Report from ground zero which includes APIs design and documentation, Unit Testing (90\% coverage), API Development, JWT Authentication, and GitLab CI/CD pipeline.}
        \item {Designed and developed Data Migration Pipeline APIs and their OpenAPI Specification that converts customer-end data to FHIR supported data using Amazon Web Services (RDS, DMS, S3, and SQS).}
        \item {Implemented Unit Testing for the Analytics APIs with a coverage report of 97\%.}
        \item {Developed Aggregation Feature in FHIR Analytics APIs.}
        \item {\textbf{Tech Used}: \textbf{Django Rest Framework}, \textbf{PostgreSQL}, \textbf{Flask}, \textbf{UnitTest}, \textbf{SQLAlchemy}, \textbf{SonarQube}, \textbf{Swagger}, and \textbf{Amazon Web Services (RDS, S3, DMS, SQS)}. }
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {\href{https://nikhil-bhasin.netlify.app/data/LetterOfExperience_InternetBullReport.pdf}{Software Engineering - Intern}} % Job title
    {\href{https://internetbullreport.com/}{Internet Bull Report Inc.}} % Organization
    {Barcelona, Spain} % Location
    {Feb. 2021 – May. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed and designed scalable web-based software solutions to solve complex business problems from scratch using Front-end and Back-end Technologies.}
        \item {Building and improving the UI/UX infrastructure and components of current websites.}
        \item {Collaborating with the team to develop UI components and on-brand design patterns.}
        \item {Deployed the web-based software solutions.}
        \item {\textbf{Tech used}: \textbf{NodeJS}, \textbf{ExpressJS}, \textbf{Mongoose}, \textbf{MongoDB}, \textbf{VanillaJS}, \textbf{Bootstrap} and \textbf{HTML/CSS}.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {\href{https://nikhil-bhasin.netlify.app/data/LetterOfExperience_CodingNinjas.pdf}{Teaching Assistant}} % Job title
    {\href{https://nikhil-bhasin.netlify.app/data/LetterOfExperience_CodingNinjas.pdf}{Coding Ninjas}} % Organization
    {New Delhi, India} % Location
    {April. 2020 – Aug. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Conducted interactive discussions with students and assisting and mentoring them through question clarification and problem-solving skills.}
        \item {Simplified 1000+ doubts of students with a 4.82/5 rating.}
        \item {\textbf{Tech Stack :} \textbf{Java}, \textbf{Data Structures} and \textbf{Algorithms}}
      \end{cvitems}
    }


\end{cventries}
