%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------

\cvsection{Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {An Online Examination Portal} % Affiliation/role
    {\href{https://github.com/phoenix-1-2/ExamOne-Server}{ExamOne Server}} % Organization/group
    {}
    {Sep. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {ExamOne is an Online Testing Platform For Conducting Remote Online Examinations.}
        \item {ExamOne is an optimised system with unique features to conduct objective, subjective as well as coding examinations online with Advanced Authentication using JWT.}
        \item {It can evaluate the examinations ( objective, subjective \& coding tests ) using machine learning algorithms, therefore, making it more convenient to use.}
        \item {\textbf{Tech Stack : Python, Django REST Framework, PostgreSQL, Cloudinary, Swagger, JSON Web Token(JWT) }}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {An E-Commerce Web Application} % Affiliation/role
    {\href{https://unistore-12.herokuapp.com/}{Unistore}} % Organization/group
    {} % Location
    {May. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Developed a real-world responsive e-commerce web app.}
        \item {It has features like Adding to Cart, Adding New Products, Getting Order Invoices(PDF),Pagination, Mailing Services and Advanced Authentication.}
        \item {\textbf{Tech Stack : JavaScript, NodeJS, ExpressJS, MongoDB, Mongoose, NodeMailer}}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Real Estate Web Application} % Affiliation/role
    {\href{https://real-estate-12-04.herokuapp.com/}{BT Real Estate}} % Organization/group
    {} % Location
    {Oct. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {It is a responsive real world web application}
        \item {It has features like Admin Panel ,Inquiry Submission Service, Advanced Searching for filtering the Real Estate based on different parameters.}
        \item {\textbf{Tech Stack : Python, Django, PostgreSQL, Javascript, HTML/CSS, jQuery}}
      \end{cvitems}
    }

%---------------------------------------------------------

 \cventry
    {Customised Food Delivery Application} % Affiliation/role
    {\href{https://app-burger-124.web.app/sign-in}{Burger Builder}} % Organization/group
    {} % Location
    {Dec. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {This is a Burger Builder App for a Restaurant to get the order from the users regarding the particular burger customized by the user.}
        \item {\textbf{Tech Stack : Javascript, ReactJS, Firebase, Material-UI, ReactStrap}}
      \end{cvitems}
    } 

%---------------------------------------------------------
\end{cventries}
